% sections.tex
% both the CV and resume share these sections

\documentclass[centered,11pt,overlapped]{res}
%\documentclass[overlapped,line,11pt,draft]{res}
%-----------------------------------------------------------------------------
\usepackage[colorlinks,urlcolor=black,bookmarks=true]{hyperref}
\usepackage[left=2cm, right=4cm, top=2cm, bottom=2cm]{geometry}
\usepackage{enumitem}


%-----------------------------------------------------------------------------
%% % To enable extended pdf support, add pdftex and the following to the
%% % hyperref \usepackage line in the [..] section:
%%
\hypersetup{
pdftitle={Dong Zhou},
pdfauthor={Dong Zhou},
pdfcreator={pdfLaTeX},
%% pdfproducer={$Id: cv-us.tex,v 1.8 2004/12/31 17:07:33 jrblevin Exp $},
pdfsubject={Curriculum Vitae},
}
%% pdfkeywords={Applied Mathematics Economics Computer Science
%%     Differential Equations TANH method hyperbolic tangent centroid
%%     decomposition updating singular value decomposition linear algebra
%%     microeconomics System Administration Linux Unix German}
%-----------------------------------------------------------------------------
\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
%-----------------------------------------------------------------------------
\begin{document}

\name{{\Large \bf Dong Zhou}}

%\address{
%}
% {\verb+http://www.physics.wisc.edu/~nos+}

\begin{resume}

\begin{ncolumn}{2}
   {\tt \href{mailto:zhou.dong@gmail.com}{zhou.dong@gmail.com}} &  (917) 207-8391 (mobile) \\
   {\tt \href{https://nosarthur.github.io}{nosarthur.github.io}} &  US green card holder
\end{ncolumn}

%------------------------------------------------------------------------------

\section{\sc Summary}
Physicist and programmer, interested in method development.
30+ papers with 2k+ citations,
Erd\"{o}s number $\le$ 5,
1k+ stars on GitHub.
Past experience includes crystal structure prediction, medical imaging, quantum computing, etc.

%------------------------------------------------------------------------------

\section{\sc Skills}
Python, Go, C, Bash, AWS/GCloud \\
Computational physics/mathematics, Image processing, Machine learning

%---------------------------------------------------------------------------
%% %% Other possible sections:
%% \section{\sc Special Skills}
%% \section{\sc Journal Publications}
%% \section{\sc Refereed Conference Proceedings}
%% \section{\sc Conference Presentations}
%------------------------------------------------------------------------------

\section{\sc Experience}

\begin{itemize}[leftmargin=-0.02in]
\item Senior Developer I then II, Schr\"odinger Inc. \hfill 2016-2024

Invented a divide-and-conquer algorithm for molecular crystal structure prediction.
        Implemented prototype for products
        (crystal packing search as optimization with Python; speedup with Cython,
        analytical gradients for geometric operations, and two-stage convergence; workflow automation with GNU Make).
Maintained atom mapping module (subgraph isomorphism) for free energy perturbation.
Implemented atom mapping schemes for lambda dynamics, fragment linking, and linker enumeration FEP (Python).
Implemented analysis library for molecular dynamics trajectories (Python, \Cplusplus).
Maintained scientific computing web services for FEP+ (aws/gcloud, Go, Python, PostgreSQL, gRPC, Docker, Polymer.js).

\item Postdoc in radiology, Weill Medical College of Cornell University \hfill 2012--2016

Invented a full multigrid solver (LBV) for background magnetic field removal.
Solved ill-posed inverse problems such as magnetic susceptibility and
susceptibility tensor imaging, magnetic quadrupole imaging, 3D phase unwrapping
(Matlab, C/\Cplusplus).
Developed probes for transcranial magnetic stimulation both in simulation (COMSOL multiphysics)
and on hardware (electronics, 3D printing).

\item Postdoc in physics, Yale University \hfill 2011--2012

Developed state preparation scheme using quantum bath engineering, and adiabatic
phase based two-qubit CNOT gate scheme on circuit QED hardware (3D transmon).
Simulated these schemes using Python package QuTip.

\item {Research assistant, University of Wisconsin-Madison} \hfill {2007--2011}

Solved open quantum systems dynamics in the presence of classical stochastic noises
both analytically and numerically (Matlab).
Developed schemes for quantum gate, quantum control, and entanglement preparation
for quantum dot systems.
Developed algorithm for graph isomorphism problem using continuous-time quantum random walk.
Performed experiments and data analyses for biological and geological samples such as nacre, pyrite, etc
(machining, X-ray diffraction, X-ray absorption near edge spectroscopy and
microscopy using synchrotron radiation @ SRC and LLNL).
Implemented GUI program for spectra analysis (KaleidaGraph).

\end{itemize}

\ite{\bl{review}}{
Reviewer for J. Phys. A, IEEE TBME, PLOS ONE, Quantum Information Processing, New J. Phys., Medicine, J. Neuroscience Methods, NeuroImage, Magnetic Resonance in Medicine, Medical Physics, NMR in Biomedicine, Int. J. Mod. Phys. B, Physica Scripta
}

\section{\sc Education}

\begin{itemize}[leftmargin=-0.02in]
\item {Ph.D in physics, University of Wisconsin-Madison (GPA 4.0, 71 credits)} \hfill {2006--2011}
\item {Graduate study in physics, University of Georgia-Athens (GPA 4.0, 49 credits)} \hfill {2004--2006}
\item {B.S. from Honored Mixed Class}, {Zhejiang University (GPA 3.8, 196 credits)} \hfill {2000--2004}
\end{itemize}

%---------------------------------------------------------------------------

\ite{\bl{awards}}{

\section{\sc Honors and Awards}
\begin{itemize}[leftmargin=-0.02in]
\item International Society for Magnetic Resonance in Medicine (ISMRM) Merit Award, Magna Cum Laude, 2014
\item International Student Academic Achievement Award, UW-Madison, 2011
\item Ray and Anne Herb Award for Wisconsin Distinguished Graduate Fellowship, 2008
\item Emanuel R. Piore Award for Highest Scorer on the Qualifier Exam, UW-Madison, 2007
\item University Housing's Favorite Instructor Award for Fall 2006, UW-Madison, 2006
\item Van Vleck Fellowship for Graduate Students in Physics, UW-Madison, 2006
\item Honored Graduate of Zhejiang University, China, 2004
\item Honorary Enrollment, Zhejiang University, China, 2000
\item Tan Jiazhen (C. C. Tan) Scholarship for Outstanding High School Student in Biology, 1999
\item Kang Hui Scholarship for Highest Scorer in High School Entrance Exam, Hangzhou, China, 1996
\end{itemize}
}

%---------------------------------------------------------------------------
\ite{\bl{patents}}{

\section{\sc Patents}
\begin{enumerate}[leftmargin=-0.02in]
\item {\em Magnetic resonance imaging systems and methods for optimized parallel receive, excite, and shim (oPRES) } \\
Hui Han, Yi Wang, John Stager, Junghun Cho, and {\bf Dong Zhou}, pending
\end{enumerate}
}

%---------------------------------------------------------------------------
\ite{\bl{pubs}}{

\section{\sc Publications}
\begin{enumerate}[leftmargin=-0.02in]
\item{\em A Robust Crystal Structure Prediction Method to Support Small Molecule Drug Development with Large Scale Validation and Prospective Studies}\\
    {\bf D. Zhou}, I. Bier, B. Santra, L. Jacobson, C. Wu, P. Skrdla, P. Devine, H. Yu, R. Abel, R. Friesner, L. Wang, ChemRxiv. (2024); submitted to Nature Communications, doi:10.26434/chemrxiv-2024-f17zp
\item{\em Quantitative susceptibility mapping of magnetic quadrupole moments}\\
J. Cho, {\bf D. Zhou}, Y. Kee, P. Spincemaille, and Y. Wang, Concepts Magn Reson Part A, 7174937 (2019)
\item{\em Cardiac Quantitative Susceptibility Mapping (QSM) for Heart Chamber Oxygenation}\\
Y. Wen, T.D. Nguyen, Z. Liu, P. Spincemaille, {\bf D. Zhou}, A. Dimov, Y. Kee, K. Deh, J. Kim, J. Weinsaft, and Y. Wang, Magn Reson Med 79 (3), 1545 (2018)
\item {\em Quantitative Susceptibility Mapping (QSM)-Based Cerebral Metabolic Rate of Oxygen Mapping with Minimum Local Variance }\\
J. Zhang, J. Cho, {\bf D. Zhou}, T.D. Nguyen, P. Spincemaille, A. Gupta, and Y. Wang, MRM 79 (1), 172 (2018)
\item {\em Susceptibility underestimation in a high susceptibility phantom: dependence on imaging resolution, magnitude contrast and other parameters}\\
{\bf D. Zhou}, J. Zhang, P. Spincemaille, Y. Wang, Magn Reson Med, 78 (3), 1080 (2017)
\item {\em Preconditioned Total Field Inversion (TFI) Method for Quantitative Susceptibility Mapping} \\
Z. Liu, Y. Kee, {\bf D. Zhou}, Y. Wang, and P. Spincemaille, Magn Reson Med 78 (1), 303 (2017)
\item {\em Cerebral Metabolic Rate of Oxygen (CMRO2) Mapping with Hyperventilation Challenge using Quantitative Susceptibility Mapping (QSM)}\\
J. Zhang, {\bf D. Zhou}, T.D. Nguyen, P. Spincemaille, A. Gupta, Y. Wang, Magn Reson Med, 77 (5), 1762 (2017)
\item {\em Three-dimensional MR Phase Unwrapping via Dual Decomposition} \\
J. Dong, F. Chen,  {\bf D. Zhou}, T. Liu, Z. Yu, and Y. Wang, Magn Reson Med 77 (3), 1353 (2017).
\item {\em On the influence of zero-padding on the nonlinear operations in Quantitative Susceptibility Mapping}\\
S. Eskreis-Winkler, {\bf D. Zhou}, T. Liu, A. Gupta, S. A. Gauthier, Y. Wang, and P. Spincemaille, MRI 35, 154 (2017)
\item {\em Quantitative susceptibility mapping and R2* measured changes during white matter lesion development in multiple sclerosis: myelin breaking down, myelin debris degradation and removal, and iron accumulation }\\
Y. Zhang, S.A. Gauthier, A. Gupta, W. Chen, J. Comunale, G.C.-Y. Chiang, {\bf D. Zhou}, G. Askin, W. Zhu, D. Pitt, Y. Wang, AJNR 37 (9) 1629 (2016).
\item {\em Longitudinal change in magnetic susceptibility of new enhanced multiple sclerosis (MS) lesions measured on serial quantitative susceptibility mapping (QSM)}\\
Y. Zhang, S.A. Gauthier, A. Gupta, J. Comunale, G. C.-Y. Chiang, {\bf D. Zhou}, W. Chen, A.E. Giambrone, W. Zhu, Y. Wang, JMRI 44 (2) 426 (2016).
\item {\em Increase in magnetic susceptibility after MS lesion formation and potential diagnostic utility} \\
Y. Zhang, S. Gauthier, L. Tu, A. Gupta, J. Comunale, G.C.-Y. Chiang, {\bf D. Zhou}, Y. Wang, Multiple Sclerosis Journal 21 502 (2016).
\item {\em Simultaneous Phase Unwrapping and Removal of chemical Shift (SPURS) using Graph Cuts: Application in Quantitative Susceptibility Mapping}\\
J. Dong, T. Liu, F. Chen, {\bf D. Zhou}, A. Dimov, A. Raj, Q. Cheng, P. Spincemaille, and Y. Wang, IEEE TMI 34 (2) 531 (2015).
\item {\em Background field removal by solving the Laplacian boundary value problem}\\
{\bf D. Zhou}, T. Liu, P. Spincemaille, and Y. Wang, NMR in Biomedicine, 27 (3), 312 (2014).
\item {\em An Iterative Spherical Mean Value (iSMV) Method for Background Field Removal in MRI}\\
Y. Wen, {\bf D. Zhou}, T. Liu, P. Spincemaille, and Y. Wang, Magn Reson Med 72 (4) 1065 (2014).
\item {\em Magnetic susceptibility anisotropy: cylindrical symmetry from macroscopically ordered anisotropic molecules and accuracy of MRI measurements using few orientations}\\
C. Wisnieff, T. Liu, P. Spincemaille, S. Wang, {\bf D. Zhou}, and Y. Wang,  NeuroImage 70, 363 (2013).
\item{\em Mediated gates between spin qubits} \\
J. Fei, {\bf D. Zhou}, Y.-P. Shim, S. Oh, X. Hu, and M. Friesen, Phys. Rev. A 86, 062328 (2012). arXiv:1207.6063
\item{\em Cavity-assisted quantum bath engineering with a superconducting qubit}\\
K. W. Murch, U. Vool, {\bf D. Zhou}, S. J. Weber, S.M. Girvin, and I. Siddiqi,
Phys. Rev. Lett. 109, 163602 (2012); arXiv:1207.0053
\item{\em Phenomenological noise model for superconducting qubits:
two-state fluctuators and 1/f noise}\\
{\bf D. Zhou} and R. Joynt, Supercond. Sci. Techno. 25, 045003 (2012); arXiv:1102.5766
\item{\em Topology of entanglement evolution of two qubits}\\
{\bf D. Zhou}, G.-W. Chern, J. Fei, and R. Joynt, Int. J. Mod. Phys. B 26, 1250054 (2012); arXiv:1007.1749
\item{\em Disappearance of entanglement: a topological point of view} \\
{\bf D. Zhou} and R. Joynt, QIP 11, 571 (2012); arXiv:1006.5474
\item{\em Suppression of decoherence and disentanglement by the exchange interaction}\\
A. De, A. Lang, {\bf D. Zhou}, and R. Joynt, Phys. Rev. A 83, 042331 (2011); arXiv:1006.5943
\item {\em Quasi-Hamiltonian Method for Computation of Decoherence Rates.}\\
R. Joynt, {\bf D. Zhou} and Q.-H. Wang, Int. J. Mod. Phys. B 25, 2115 (2011); arXiv:0906.2843
\item {\em Noise-induced looping on the Bloch sphere: Oscillatory effects in dephasing of qubits subject to broad-spectrum noise.}\\
{\bf D. Zhou} and R. Joynt, Phys. Rev. A 81, 010103 (2010); arXiv:0907.0463
\item {\em Nacre Protein Fragment Templates Lamellar Aragonite Growth}\\
RA Metzler, JS Evans, CE Killian, {\bf D Zhou}, TH Churchill, N Appathurai, SN Coppersmith, PUPA Gilbert, J. Am. Chem. Soc. 132, 6329-6334 (2010).
\item {\em X-ray photoelectron emission spectromicroscopic analysis of arborescent lycopsid cell wall composition and Carboniferous coal ball preservation.}\\
C. K. Boyce, M. Abrecht, {\bf D. Zhou}, and P.U.P.A. Gilbert, Int. J. Coal Geol. 83, 146-153 (2010).
\item {\em Disentanglement and decoherence from classical non-Markovian noise: Random telegraph noise.}\\
{\bf D. Zhou}, A. Lang, and R. Joynt, QIP 9, 727 (2010); arXiv:0912.3313
\item {\em Two-particle quantum walks applied to the graph isomorphism problem.} \\
J. Gamble, M. Friesen, {\bf D. Zhou}, R. Joynt, and S.N. Coppersmith, Phys. Rev. A 81, 052313 (2010); arXiv:1002.3003
\item {\em A high-resolution chemical and structural study of framboidal pyrite formed within a low-temperature bacterial biofilm.}\\
L.C.W. MacLean, T. Tyliszczak, P.U.P.A. Gilbert, {\bf D. Zhou}, T.J. Pray, T.C. Onstott, G. Southam.  Geobiology 6, 471-480 (2008).
\item {\em Gradual Ordering in Red Abalone Nacre.}\\
P.U.P.A. Gilbert, R. A. Metzler, {\bf D. Zhou}, A. Scholl, A. Doran, A. Young, M. Kunz, N. Tamura, S. N. Coppersmith. J. Am. Chem. Soc. 130, 17519-17527 (2008); arXiv:0710.4573
\item {\em Assignment of polarization-dependent peaks in carbon K-edge spectra from biogenic and geologic aragonite.}\\
{\bf D. Zhou}, R.A. Metzler, T. Tyliszczak, J. Guo, M. Abrecht, S.N. Coppersmith, P.U.P.A. Gilbert. J. Phys. Chem. B 112, 13128-13135 (2008).
\item {\em Probing the organic-mineral interface in model biominerals.}\\
R. A. Metzler, I.-W. Kim, K. Delak, J.S. Evans, {\bf D. Zhou}, E. Beniash, F. Wilt, M. Abrecht, J.-W. Chiou, J. Guo, S.N. Coppersmith, P.U.P.A. Gilbert.  Langmuir 24, 2680-2687 (2008).
\item {\em Polarization-dependent imaging contrast in abalone shells.}\\
R.A. Metzler, {\bf D. Zhou}, M. Abrecht, J.-W. Chiou, J. Guo, D. Ariosa, S.N. Coppersmith, P.U.P.A. Gilbert. Phys. Rev. B 77, 064110 (2008).
\end{enumerate}

}

%------------------------------------------------------------------------------

%==============================================================================
%\newpage
%\opening
%---------------------------------------------------------------------------

%%\vspace{\fill}\ \newline
%%{\tiny \rm $ $RCSfile: cv-us.tex,v $ $ }
%%{\tiny \rm $ $Date: 2004/12/31 17:07:33 $ $ }
%%{\tiny \rm $ $Revision: 1.8 $ $ }

%------------------------------------------------------------------------------

\ite{\bl{ref}}{

%\newpage
%\opening
\section{\sc References}

%
Reference A. Person \newline
Sandia National Laboratories \newline
000-000-0000 \newline
{\tt devnull@Sandia.GOV} \newline
Impressive Title for Person


%
Reference A. Person \newline
Sandia National Laboratories \newline
000-000-0000 \newline
{\tt devnull@Sandia.GOV} \newline
Impressive Title for Person

}

\end{resume}

\end{document}
