%% $Id: cv-us.tex,v 1.8 2004/12/31 17:07:33 jrblevin Exp $
%%----------------------------------------------------------------------------
%% The layout of this resume is based on Michael Forman's CV template
%% at http://www.Michael-Forman.com/vitae/.  I have modified his template
%% to work with LaTeX 2e using res.cls instead of res.sty.  I have also
%% included the hyperref package for including hypertext links in pdfs.
%%
%% Content is Copyright (C) 2004 Jason Blevins <jrblevin@sdf.lonestar.org>
%%----------------------------------------------------------------------------
%% To Do:
%%   * Get the pdf information section working with latex 2e
%%   * Add descriptions of Phi Beta Kappa and Phi Kappa Phi
%%   * Update address and telephone number
%%   * Add more details about positions
%%----------------------------------------------------------------------------
\RequirePackage{ifthen}
\newcommand{\ite}{\ifthenelse}
\newcommand{\bl}{\boolean}
%-----------------------------------------------------------------------------
\newboolean{ref}
\setboolean{ref}{false}
\newboolean{skill}
\setboolean{skill}{false}
\newboolean{pubs}
\setboolean{pubs}{true}
\newboolean{talk}
\setboolean{talk}{false}
\newboolean{member}
\setboolean{member}{false}


\documentclass[centered,11pt,overlapped]{res}
%\documentclass[overlapped,line,11pt,draft]{res}
%-----------------------------------------------------------------------------
\usepackage[colorlinks,urlcolor=black,bookmarks=true]{hyperref}
\usepackage{enumitem}


%-----------------------------------------------------------------------------
%% % To enable extended pdf support, add pdftex and the following to the
%% % hyperref \usepackage line in the [..] section:
%%
\hypersetup{
pdftitle={Curriculum Vitae},
pdfauthor={Dong Zhou},
%% pdfcreator={pdfLaTeX},
%% pdfproducer={$Id: cv-us.tex,v 1.8 2004/12/31 17:07:33 jrblevin Exp $},
pdfsubject={Curriculum Vitae},
}
%% pdfkeywords={Applied Mathematics Economics Computer Science
%%     Differential Equations TANH method hyperbolic tangent centroid
%%     decomposition updating singular value decomposition linear algebra
%%     microeconomics System Administration Linux Unix German}
%-----------------------------------------------------------------------------
\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
%-----------------------------------------------------------------------------
\begin{document}

\name{{\Large \bf Dong Zhou}}

%\address{
%}
%\address{
%}
% {\verb+http://www.physics.wisc.edu/~nos+}

\begin{resume}

\begin{ncolumn}{2}
   {\tt zhou.dong@gmail.com} &  (917) 207-8391 (mobile) \\
   {\tt \href{nosarthur.github.io}{nosarthur.github.io}} &  with work authorization in US
\end{ncolumn}

%------------------------------------------------------------------------------

\section{\sc Summary}
A scientist and programmer. 
Looking for opportunities in applying machine learning to solve social problems, especially in healthcare and education.
Past experience includes image processing, mathematical modeling, computational mathematics/physics, stochastic process. Familiar with magnetic resonance imaging, quantum computing and biophysics.

%------------------------------------------------------------------------------

\section{\sc Skills}
Python, Matlab, C/\Cplusplus, Linux shell scripts, d3.js, SQL \\
Machine learning, Image processing, computational physics/mathematics\\
Mathematical modeling, Optimization with regularization, Stochastic process 
\ite{\bl{pubs}}{        

\begin{format}
\title{l}\dates{r}\\
\employer{l}\location{r}\\
%\body\\
\end{format}

%---------------------------------------------------------------------------

\section{\sc Experience}

\begin{itemize}
\item Postdoc in radiology, Weill Medical College of Cornell University \hfill 2012--2016 

Solving ill-posed inverse problems in medical imaging using Matlab, C and \Cplusplus.
Developing probes for transcranial magnetic stimulation.
\item Postdoc in physics, Yale University \hfill 2011--2012

Simulating solid state quantum optics (circuit QED) systems using Python. 
Developing schemes for quantum control and quantum gate.
\item {Research assistant, University of Wisconsin-Madison} \hfill {2007--2011} 

Studying quantum systems in the presence of classical noises using Matlab and \Cplusplus.
Developing scheme for quantum gate. 
Developing algorithm for graph isomorphism problem.
Performing X-ray diffraction and synchrotron radiation experiments on nacre (mother of pearl) and other samples.
\item {Teaching assistant, University of Wisconsin-Madison} \hfill {2006--2006} 

Teaching introductory physics courses.
\item {Teaching assistant, University of Georgia-Athens} \hfill {2004--2006} 

Teaching introductory physics courses.


\section{\sc Education}
\item {Ph.D in physics, University of Wisconsin-Madison} \hfill {2006--2011} 
\item {Graduate study in physics, University of Georgia-Athens} \hfill {2004--2006}  
\item {B.S. in physics, Honored Mixed Class},  
{Zhejiang University, China } \hfill {2000--2004}  
\end{itemize}


%---------------------------------------------------------------------------

\section{\sc Honors and Awards}
\begin{itemize}[leftmargin=-0.1in]
\item International Society for Magnetic Resonance in Medicine (ISMRM) Merit Award, magna cum laude, 2014
\item International Student Academic Achievement Award, UW-Madison, 2011
\item Ray and Anne Herb Award for Wisconsin Distinguished Graduate Fellowship, 2008
\item Emanuel R. Piore Award for Highest Scorer on the Qualifier Exam, UW-Madison, 2007
\item University Housing's Favorite Instructor Award for Fall 2006, UW-Madison, 2006
\item Van Vleck Fellowship for Graduate Students in Physics, UW-Madison, 2006
\item Honored Graduate of Zhejiang University, China, 2004
\item Honorary Enrollment, Zhejiang University, China, 2000
\item Tan Jiazhen (C. C. Tan) Scholarship for Outstanding High School Student in Biology, 1999
\item Kang Hui Scholarship for Highest Scorer in High School Entrace Exam, Hangzhou, China, 1996
\end{itemize}


%---------------------------------------------------------------------------
\section{\sc Publications and Services}
Author for 27 journal articles and reviewer for 11 journals.
}
%------------------------------------------------------------------------------


\end{resume}

\end{document}
